The Birth of a Galaxy: Primoridal Metal Enrichment and Population II Stellar Populations

### 2010-11-08 ms.tex
Renamed figures to be f[1-4].eps
Applying changes that I forgot to pull.

Numerical simulations are useful to detangle and study these
complexities and the transition from Pop III to II stars.  In this
Letter, we present the simulations that include both types of SF, and
their radiative and mechanical feedback.  The methods used here
incorporate and link together recent results from metal-enriched and
metal-free star formation, the critical metallicity, and
pair-instability supernovae.  This is the first time it has been
possible to link the formation and feedback of the first stars to
protogalaxies, resolving the important scales and including the most
important physical effects.  We describe our simulation setup and our
adopted SF models in \S \ref{sec:setup} and present our results in \S
\ref{sec:results}.  We discuss the implications of our findings and
conclude in the last section.

@@

\begin{figure}
\epsscale{1.15}
\plotone{Lstar.eps}
\epsscale{1}
\caption{\label{fig:massfn} \textit{Top}: Halo mass function of the
  simulation compared with the analytical fit (solid) of
  \citet{Warren06}.  \textit{Bottom}: Total Pop II luminosities of
  halos with constant mass-to-light ratios overplotted.}
\end{figure}

@@

\begin{figure*}
\epsscale{1.15}
\plotone{f1.eps}
\epsscale{1}
\caption{\label{fig:projections} Density-weighted projections of gas
  density (top), temperature (middle), and metallicity (bottom) at
  $z=7$.  The left column shows the entire simulation volume, where
  the center and right columns focus on the intense and quiet halos,
  which are marked by left and right arrows in the upper-left panel.
  The metallicity projections are a composite picture of metals
  originating from Pop III (red) and Pop II (blue) stars with magenta
  indicating a mixture of the two.}
\end{figure*}

@@

\begin{figure*}
\epsscale{1.15}
\plotone{f2.eps}
\epsscale{1}
\caption{\label{fig:evo} (a) Evolution of the total halo mass (top),
  stellar mass (middle), and gas fraction (bottom) of the quiet
  (dashed) and intense (solid) halos.  (b) Mass-weighted stellar
  metallicities and gas metallicities enriched by Pop II and Pop III
  SNe of the intense (top) and quiet (bottom) halos.}
\end{figure*}

@@

\begin{figure*}
\epsscale{1.1}
\plotone{f3.eps}
\epsscale{1}
\caption{\label{fig:pops} The scatter plots show the SF history of the
  quiet (left) and intense (right) halos as a function of metallicity
  at $z=7$.  Each circle represents a star cluster, whose area is
  proportional to its mass.  The open circles in the upper right
  represent sizes of $10^3$, $10^4$, and $10^5$ \Ms~star clusters.
  The dashed lines in the right panel guide the eye to two stellar
  populations that were formed in two satellite halos, merging at
  $z=7.5$.  The upper histogram shows the SF rate.  The right
  histogram depicts the stellar metallicity distribution.}
\end{figure*}

@@

In this Letter, we focus on the birth of two galaxies prior to
reionization with a cosmological AMR radiation hydrodynamics
simulation.  Supernovae from Pop III stars provide the necessary heavy
elements for the transition to a Population II stellar population,
which we have directly simulated.  These two galaxies have a 10--15\%
probability in surviving as present-day ``fossil'' galaxies
\citep{Gnedin06}, otherwise they will be incorporated into galactic
stellar halos.  A $z=8.55$ galaxy was recently spectroscopically
confirmed that is contained in an ionized bubble with radius 0.1--0.5
Mpc with an uncharacterized population of galaxies contributing to the
local ionizing radiation field \citep{Lehnert10_z8.6}.  The galaxies
simulated here might represent this population.

>>>>

Numerical simulations are useful to detangle and study these
complexities and the transition from Pop III to II stars.  In this
Letter, we present a simulation that includes both types of SF, and
their radiative and mechanical feedback.  The methods used here
incorporate and link together recent results from metal-enriched and
metal-free star formation, the critical metallicity, and
pair-instability supernovae.  This is the first time it has been
possible to link the formation and feedback of the first stars to
protogalaxies, resolving the important scales and including the most
important physical effects.  We describe our simulation setup and our
adopted SF models in \S \ref{sec:setup} and present our results in \S
\ref{sec:results}.  We discuss the implications of our findings and
conclude in the last section.

@@

\begin{figure}
\epsscale{1.15}
\plotone{f1}
\epsscale{1}
\caption{\label{fig:massfn} \textit{Top}: Halo mass function of the
  simulation compared with the analytical fit (solid) of
  \citet{Warren06}.  \textit{Bottom}: Total Pop II luminosities of
  halos with constant mass-to-light ratios overplotted.}
\end{figure}

@@

\begin{figure*}
\epsscale{1.15}
\plotone{f2}
\epsscale{1}
\caption{\label{fig:projections} Density-weighted projections of gas
  density (top), temperature (middle), and metallicity (bottom) at
  $z=7$.  The left column shows the entire simulation volume, where
  the center and right columns focus on the intense and quiet halos,
  which are marked by left and right arrows in the upper-left panel.
  The metallicity projections are a composite picture of metals
  originating from Pop III (red) and Pop II (blue) stars with magenta
  indicating a mixture of the two.}
\end{figure*}

@@

\begin{figure*}
\epsscale{1.15}
\plotone{f3}
\epsscale{1}
\caption{\label{fig:evo} (a) Evolution of the total halo mass (top),
  stellar mass (middle), and gas fraction (bottom) of the quiet
  (dashed) and intense (solid) halos.  (b) Mass-weighted stellar
  metallicities and gas metallicities enriched by Pop II and Pop III
  SNe of the intense (top) and quiet (bottom) halos.}
\end{figure*}

@@

\begin{figure*}
\epsscale{1.1}
\plotone{f4}
\epsscale{1}
\caption{\label{fig:pops} The scatter plots show the SF history of the
  quiet (left) and intense (right) halos as a function of metallicity
  at $z=7$.  Each circle represents a star cluster, whose area is
  proportional to its mass.  The open circles in the upper right
  represent sizes of $10^3$, $10^4$, and $10^5$ \Ms~star clusters.
  The dashed lines in the right panel guide the eye to two stellar
  populations that were formed in two satellite halos, merging at
  $z=7.5$.  The upper histogram shows the SF rate.  The right
  histogram depicts the stellar metallicity distribution.}
\end{figure*}

@@

In this Letter, we focus on the birth of two galaxies prior to
reionization with a cosmological AMR radiation hydrodynamics
simulation.  Supernovae from Pop III stars provide the necessary heavy
elements for the transition to a Population II stellar population,
which we have directly simulated.  These two galaxies have a 10--15\%
probability in surviving as present-day ``fossil'' galaxies
\citep{Gnedin06}, otherwise they will be incorporated into galactic
stellar halos.  A $z=8.55$ galaxy was recently spectroscopically
confirmed that is contained in an ionized bubble with radius 0.1--0.5
Mpc with an uncharacterized population of galaxies contributing to the
local ionizing radiation field \citep{Lehnert10_z8.6}.  The galaxies
simulated here might represent this population and should be detected
with the upcoming \textit{James Webb Space Telescope}.
